
\begin{thebibliography}{1000}
\addcontentsline{toc}{section}{Литература}

% ---
% Введение

\bibitem[Азиз2004]{aziz_2004} 
Азиз Х., Сеттари Э.  Математическое
моделирование пластовых систем.  Институт компьютерных исследований,
Москва-Ижевск, 2004, 416 с.

\bibitem[Борисов2017]{borisov_2017} 
Азиз Х., Сеттари Э.  Математическое
моделирование пластовых систем.  Институт компьютерных исследований,
Москва-Ижевск, 2004, 416 с.

\bibitem[Biot1941]{biot_1941}
Борисов В.Е., Иванов А.В., Критский Б.В., Меньшов И.С., Савенков Е.Б. Численное  моделирование задач
пороупругости. Препринты ИПМ им. М.В.Келдыша. 2017. №81. 
36 с.

\bibitem[Brezzi1991]{brezzi1991}
Brezzi~F., Fortin~M. Mixed and Hybrid Finite Elements Methods.
Springer, 1991.

\bibitem[Chappele1993]{chappele1993}
Chappele~D., Bathe~K.J.
The $\inf$-$\sup$ Test //
\emph{Computers \& Structures}, 1993.
V.~47, \No~4--5, pp.~537--545.

\bibitem[Cheng1988]{cheng_1988}
Cheng~A.H-D., Detournay~E. 
A direct boundary element method for plane strain
poroelasticity // \emph{Int. J. Num. Anal. Meth. Geomech.}, 12, pp. 551--572, 1988.

\bibitem[Cleary1994]{cleary1994}
Cleary M.P., Quinn. T.S., C.J. de Pater.
Experimental Verification of Dimensional Analysis for Hydraulic Fracturing // 
SPE Production \& Facilities, November 1994.
pp.~230--238

\bibitem[Commend2004]{commend2004}
Commend~S., Truty~A.,  Zimmermann~Th.
Stabilized finite elements applied to elastoplasticity: I. Mixed displacement–pressure formulation //
\emph{Comput. Methods Appl. Mech. Engrg.}, 2004.
V.~193, pp.~3559--3586.

\bibitem[Coussy2004]{coussy_2004}
Coussy~O. Poromechanics, John Wiley and Sons, 2004.

\bibitem[Detournay1993]{detournay_1993}
Detournay~E., Cheng~ A.H.-D. 
Fundamentals of poroelasticity.
Chapter 5 in Comprehensive Rock Engineering: Principles, Practice and Projects, Vol. II, Analysis and
Design Method, ed. C. Fairhurst, Pergamon Press, 1993, pp.~113--171.

\bibitem[Ern2009]{ern2009}
Ern~A., Meunier~S.
A-posteriori error analysis of Euler-Galerkin
approximations to coupled elliptic-parabolic problems // \emph{ESAIM: M2AN}, 2009.
V.~43, \No~2, pp.~353--375.

\bibitem[Haga2012]{haga2012}
Haga~J.B., Osnes~H., Langtangen~H.P.
On the causes of pressure oscillations in low-permeable and low-compressible porous media //
\emph{Int. J. Numer. Anal. Meth. Geomech.}, 2012.
V.~36, \No~12, pp.~1507--1522.

\bibitem[Kim2009]{kim2009}
Kim~J., Tchelepi~H.A., Juanes~R. Stability, Accuracy and Efficiency of Sequential Methods
for Coupled Flow and Geomechanics // SPE Paper 119084, 2009. 

\bibitem[Kim2010]{kim2010}
Kim~J. Sequentual Methods for Coupled Geomechanics and Multiphase Flow //
PhD Thesis, Stanford University, 2010, 274~p.

\bibitem[Lewis1998]{lewis1998}
Lewis~R.W., Schrefler~B.A. The Finite Element
Method in the Static and Dynamic Deformation and Consolidation in
Porous Media. J. Wiley, Chichester, 2nd ed., 1998.

\bibitem[Mandel1953]{mandel_1953}
Mandel~J. Consolidation des sols (itude mathimatique) // \emph{Gbotechnique}, 1953, pp.~287--299.

\bibitem[Murad1996]{murad1996}
Murad~M.A., Thomee~V., Loula~A.F.D.
Asymptotic Behavior of Semidiscrete Finite-Element Approximations of Biot's Consolidation
Problem // \emph{SIAM Journal on Numerical Analysis}, 1996.
V.~33, \No~3, pp.~1065--1083.

\bibitem[Noorishad1982]{noorishad1982}
Noorishad~J., Ayatollahi~M.S., Witherspoon~P.A.
A Finite-Element Method for Coupled
Stress and Fluid Flow Analysis in
Fractured Rock Masses // \emph{J. Rock Mech. Min. Sol \& Geomech.}, 1982.
V.~19, pp.~185--193.

\bibitem[Philips2005]{philips2005}
Philips~B.A.
Finite Element Methods in Linear Poroelasticity:
Theoretical and Computational Results // PhD Thesis, The University of Texas at Austin, 2005, 284~p.

\bibitem[Philips2009]{philips2009}
Phillips~P.J., Wheeler~M.F.
Overcoming the problem of locking in linear elasticity
and poroelasticity: an heuristic approach // \emph{Comput. Geosci.}, 2009.
V.~13, pp.~5--12.

\bibitem[Preisig2011]{preisig2011}
Preisig~M., Pr\'vost~J.H.
Stabilization procedures in coupled poromechanics problems:
A critical assessment // \emph{Int. J. Numer. Anal. Meth. Geomech.}, 2011.
V.~35, pp.~1207--1225.

\bibitem[Showalter2000]{showalter2000}
Showalter R.E.
Diffusion in Poro-Elastic Media // \emph{Journal of Mathematical Analysis and Applications}, 2000.
V.~251, \No~1, pp.~310--340.

\bibitem[Terzaghi1996]{terzaghi_1996}
Terzaghi~K. Soil mechanics in engineering practice. John Wiley \& Sons, 1996.

\bibitem[Trimonova2017]{trimonova2017}
Trimonova~M., Baryshnikov~N., Zenchenko~E., Zenchenko~P., Turuntaev~S.
The Study of the Unstable Fracure Propagation in the Injection Well: Numerical and Laboratory Modeling. // 
Society of Petroleum Engineers, 2017, October 16. 
Conference paper. 187822-MS. 

\bibitem[Trimonova2018]{trimonova2018}
Trimonova~M., Baryshnikov~N., Zenchenko~E., Zenchenko~P., Turuntaev~S., Aigozhieva~A.
Estimation of the Hydraulic Fracture Propagation Rate in the Laboratory Experiment. // 
Physical and Mathematical Modeling of Earth and Environment Processes. 2018.

\bibitem[Vermeer1981]{vermeer1981}
Vermeer~P.A., Verruijt~A.
An Accuracy condition for Consolidation by Finite Elements //
\emph{Int. J. Numer. Anal. Meth. Geomech.}, 1981. V.~5, pp.~1--14.

\bibitem[Wan2002]{wan2002}
Wan~J. Stabilized Finite Element Method for Coupled Geomechanics and  Multiphase Flow //
PhD Thesis, Stanford Univeristy, 2002, 180~p.

\bibitem[Wang2000]{wang_2000}
Wang~H.F. Theory of Linear Poroelasticity, Princeton University Press, 2000.

\bibitem[White2008]{white2008}
White~J.A., Borja~R.I. 
Stabilized low-order finite elements for coupled solid-deformation/fluid-diffusion and their application to fault zone transients //
\emph{Comput. Methods Appl. Mech. Engrg.}, 2008.
V.~197, \No~49--50, pp.~4353--4366.

\bibitem[Wieners2003]{wieners2003} 
Wieners~C.
Taylor-Hood elements in 3D // in Analysis and Simulation of Multifield Problems, 
Wolfgang L. Wendland, Messoud Efendiev, Lecture Notes in Applied and Computational Mechanics, Springer, 2003.
V.~12, 381~p.

\bibitem[Xia2009]{xia2009}
Xia~K., Masud~A.
A stabilized finite element formulation for finite deformation
elastoplasticity in geomechanics // \emph{Computers and Geotechnics}, 2009.
V.~36, pp.~396--405.

\bibitem[Zheng2003]{zheng2003}
Zheng~Y., Burridge~R., Burns~D.
Reservoir Simulation with the Finite Element Method Using Biot Poroelastic Approach // 
Earth Resources Laboratory Industry Consortia Annual Report 2003-11, 
Massachusetts Institute of Technology. Earth Resources Laboratory, 2003, 20~p.

%%%%%%%%%%%%%%%%%%%%%%%%
\end{thebibliography}

\endinput
%%%%
% EOF
